---
title: "BBets Project"
author: "Nadezda Carr"
date: "2/1/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The question is how much money is one lost in a bet that at least 2 people have the same birthday in class of 35. Intructor wager is 2:1. 

Instructor has done this 15 times.
1. What is expected loss/win?

amount  
2. How much would the instructor have to wager to make the bet fair.
3. how many students have to be in the class for a 2:1 bet to be fair?

```{r}
days = 1:365

students = 35
classes = 15
runs = students * classes
payout = 2

saveArray=vector('numeric')
for (k in 1:1000){

  bank = 0
  for (i in 1:runs){
    sampleClass = sample(days, students, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == 35) bank = bank - payout
    else bank = bank + 1
  }
saveArray[k]= bank
}
```
  

histogram of bank amounts.

```{r}
hist(saveArray)
```
Answer question #1

```{r}
print('average amt:')
print(mean(saveArray))
```

#2

```{r}
days = 1:365

students = 35
classes = 15
runs = students * classes
payout = 4.39

saveArray=vector('numeric')
for (k in 1:1000){

  bank = 0
  for (i in 1:runs){
    sampleClass = sample(days, students, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == 35) bank = bank - payout
    else bank = bank + 1
  }
saveArray[k]= bank
}

```

histogram of bank amounts.

```{r}
hist(saveArray)
```
Answer Question 2

```{r}
print('Instructor Wager')
print(payout)

print('average amount')
print(mean(saveArray))
```

 #3

```{r}
days = 1:365

students = 29
classes = 15
runs = students * classes
payout = 2

saveArray=vector('numeric')
for (k in 1:1000){

  bank = 0
  for (i in 1:runs){
    sampleClass = sample(days, students, replace = TRUE)

    repeats = length(unique(sampleClass))
    if (repeats == students) bank = bank - payout
    else bank = bank + 1
  }
saveArray[k]= bank
}

```

histogram of bank amounts.

```{r}
hist(saveArray)
```
Answer #3

```{r}
print('Student Count')
print(students)
print('average amount')
print(mean(saveArray))

```

